---
title: "Update figures!"
author: "B. Steele"
date: "2024-03-14"
output: html_document
---

This script updates figures created in this repository using the most recent
data published via the LMP. 

```{r setup}
# list packages used in the scripts
packages <- c("tidyverse",
              "ggthemes",
              "gghighlight",
              "sf",
              "tmap",
              "raster",
              "gifski", 
              "cowplot",
              "devtools",
              "readxl",
              "httr")

# function to check for install packages
check_install_packages <- function(package) {
  if (package %in% rownames(installed.packages()) == FALSE) {
    install.packages(package)
  }
}

# install all packages!
lapply(packages, check_install_packages)

# the ggsflabel package contains geom_sf_repel to make pretty labels
devtools::install_github("yutannihilation/ggsflabel")

library(tidyverse)
library(readxl)
library(httr)
```


# Point to the most recent data

These are all publically available data. When updating, you'll need to update the version.

```{r}
# read in LMP record
lmp <- read.csv('https://raw.githubusercontent.com/Lake-Sunapee-Protective-Association/LMP/main/primary%20files/LSPALMP_1986-2023_v2024-01-20.csv')

lmp_locs <- read.csv('https://raw.githubusercontent.com/Lake-Sunapee-Protective-Association/LMP/main/primary%20files/station_location_details.csv') %>% 
  mutate(sub_site_type = case_when(site_type == 'tributary' ~ 'tributary',
                                   TRUE ~ sub_site_type))


xls_names_url <- 'https://raw.githubusercontent.com/Lake-Sunapee-Protective-Association/LMP/main/raw%20data%20files/station%20locations/Cove%20%20Deep%20+%20Buoy%20WQ%20Sample%20Point%20GPS%20Coordinates.xls'
GET(xls_names_url, write_disk(tf <- tempfile(fileext = ".xls")))
lmp_lake_names <- read_xls(tf,
                           skip = 3) %>% 
  rename(station = WAYPOINT) %>% 
  select(station, Name) %>% 
  filter(station != 'Buoy' & station != '100.09999999999999') %>% 
  mutate(station = as.numeric(station))
unlink(tf)

xls_tribs_url <- "https://raw.githubusercontent.com/Lake-Sunapee-Protective-Association/LMP/main/raw%20data%20files/station%20locations/tributary_pts_alt.xls"
GET(xls_tribs_url, write_disk(tf <- tempfile(fileext = ".xls")))
lmp_trib_names <- read_xls(tf) %>% 
  rename(station = stream_no,
         Name = stream_name) %>% 
  select(station, Name)
unlink(tf)

names <- full_join(lmp_lake_names, lmp_trib_names)

lmp_shortlist <- lmp_locs %>% 
  filter(first_year < 1995 & status == "ongoing") %>% 
  left_join(., names) 

lmp_shortlist <- lmp_shortlist %>% 
  filter(!is.na(Name)) %>% 
  mutate(Name = paste0(station, ' - ', Name)) 

```

# Point to the output directory and the GIS folder

```{r}
# where you want your figures to get saved (this directory must exist!)
gen_dump_dir <- 'C:/Users/steeleb/Dropbox/Lake Sunapee/misc/state of the lake/figs/'

#  where the GIS files are stored
feat_dir <- 'C:/Users/steeleb/Dropbox/travel/gis/project/Sunapee/'
```

# Run the summary files

These scripts create annual summaries for each of the parameters. Since data handling may be different across parameters, we run these individually.

```{r}
summary_scripts = c("chla_summary.R", 
                    "chloride_summary.R",
                    "conductivity_summary.R",
                    "phosphorus_summary.R",
                    "turbidity_summary.R")

map(summary_scripts, source)
```


```{r}
# name the range for the 10-year plots (2014 for 2014-2023, so forth)
start_10_year = 2014
end_10_year = 2023
```

Figs scripts that have been adjusted to use this mechanism for update

```{r}
source("phosphorus_simplefigs.R")
source("turbidity_simplefigs.R")
```


Maps scripts that have been adjusted to use this mechanism for update

```{r}
source("phosphorus_snapshotmaps.R")
source("phosphorus_maps.R")
source("turbidity_snapshotmaps.R")
```

